Demonstration of matching route networks

### 2024-01-30 r/data-raw/test-large-edinburgh.qmd

```

>>>>

```
```{r}
x <- open_roads |> 
  dplyr::transmute(n = seq(nrow(open_roads))) |> 
  sf::st_transform("EPSG:27700") |> 
  sf::st_cast("LINESTRING")

y <-  osm_roads |> 
  sf::st_cast("LINESTRING") |> 
  sf::st_zm() |> 
  sf::st_transform("EPSG:27700")

res <- rnet_match(
  x, y,
  dist = 200,
  angle_tolerance = 10,
  trees = "xy"
)

head(res)
```
